---
title: "Assignment1"
author: "Kowshik Sarker"
date: "7/19/2020"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Github Repo Link - "https://github.com/kowshiksarker/IBA-Repo"

## 1.From the USJudgeRatings dataset find the mean and standard delivation of the oevrall ratings of the judges

```{r,echo=TRUE}
overallratings<-USJudgeRatings
overallratings<-transform(overallratings,Mean=apply(overallratings,1,mean),SD=apply(overallratings,1,sd))
overallratings<-as.data.frame(overallratings[,c(13:14)])
overallratings
```

## 2.Read the Aids2.csv file
Before reading the file we need to set our working directory by setwd() command and keep the file in this directory and then execute the below commands.
```{r,echo=TRUE}
aids<- read.csv("Aids2.csv")
head(aids)
```

## 3.Create a subset of the data without the state "Other"
```{r,echo=TRUE}
subset_aids<-subset(aids,aids$state!="Other")
head(subset_aids)
```

## 4.Add a new variable called 'agebracket'
## if age is below 20, agebracket is "0-20"
## if age is between 20 to 40, agebracket is "20-40"
## if age is between 40 to 60, agebracket is "40-60"
## if age is above 60, agebracket is ">60"

```{r,echo=TRUE}
subset_aids$agebracket<-ifelse(subset_aids$age<"20",c("0-20"),
                               ifelse(subset_aids$age>="20" & subset_aids$age<"40",c("20-40"),
                                      ifelse(subset_aids$age>="40" & subset_aids$age<="60",c("40-60"),
                                             ifelse(subset_aids$age>"60",c(">60"),"NA"))))
      
head(subset_aids)
```

## 5.Sort the data from high to low based on the variable "diag" and then low to high based on "death"
```{r,echo=TRUE}
subset_aids<-subset_aids[order(-subset_aids$diag,subset_aids$death),]
head(subset_aids)
```

## 6.Calculate and add one more variable which is (diag^2/death) and name it as "dd"
```{r,echo=TRUE}
subset_aids$dd<-subset_aids$diag^2/subset_aids$death
head(subset_aids)
```

## End Of The Assignment